---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

rd2md <- function(rd) {
  html <- capture.output(tools::Rd2HTML(tools::parse_Rd(rd)))
  md <- system2("pandoc", "-f html -t gfm", stdout = TRUE, input = html)

  # remove header

  title <- grep("^## ", md)[1]
  md <- md[-seq_len(title - 1)]

  # remove empty lines between list items

  items <- grep("^  - ", md)
  gaps <- items[which(diff(items) == 2)] + 1
  gaps <- gaps[md[gaps] == ""]

  if (length(gaps)) {
    md <- md[-gaps]
  }

  # move all headings down by one level

  md <- sub("^#", "##", md)

  # mark code blocks as R code

  code <- grep("^ {4}", md)
  start <- code[diff(c(-1, code)) > 1]
  end <- code[diff(c(code, Inf)) > 1]

  for (i in seq_along(start)) {
    md <- append(md, "``` r", after = start[i] - 1 + 2 * (i - 1))
    md <- append(md, "```", after = end[i] + 1 + 2 * (i - 1))
  }

  md <- sub("^ {4}", "", md)

  cat(md, sep = "\n")
  return(invisible(md))
}
```

# bamlssGP

> Gaussian process responses for the bamlss package

<!-- badges: start -->
<!-- badges: end -->

This R package implements different Gaussian processes as response distribution families for the bamlss package, i.e. for Bayesian additive models for location, scale, and shape. It also provides an efficient MCMC sampler for these models.

Take a look at the help pages below to get a better idea of what the package does.

## Installation

You can install the development version of bamlssGP from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hriebl/bamlssGP")
```

## Help pages

```{r man1, echo = FALSE, results = "asis"}
rd2md("man/gp_constant_bamlss.Rd")
```

```{r man2, echo = FALSE, results = "asis"}
rd2md("man/sample_bamlss_gp.Rd")
```
